On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2024-01-10 Manuscript/manuscript.tex
allow breaks

We generated time series $X_t$ from a 1st 
order autoregressive (AR(1)) process:
\begin{equation*}
X_t = \phi X_{t-1} + \epsilon_t,
\end{equation*}
where $\phi$ is an autoregressive coefficient, and $\epsilon_t$ is a series of
independent errors from a normal distribution with mean zero and variance
$\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
$\phi$, which was set to five levels: $\{-0.4, -0.2, 0.0, 0.2, 0.4\}$. We only
used serial dependences as strong as 0.4, because we only seek to 
establish the 
general trend as the strength of the autocorrelation 
increases, and how it varies depending on the sign of the autocorrelation and 
the parameter of interest. The 
series $X_t$ has mean zero and variance 
$\sigma_x^2 = (1 - \phi^2) \sigma_{\epsilon}^2$, so for each value of $\phi$, we 
set $\sigma_{\epsilon}^2 = 1 / (1 - \phi^2)$ such that $\sigma_x^2 = 1$.

@@

The series were generated by marginally transforming the
AR(1) series $X_t$ in the first simulation study by
\begin{equation*}
W_t = F^{-1}[\Phi(X_t)],
\end{equation*}
where $F^{-1}(p)$ is the quantile function for the unit exponential 
distribution. The true mean ($\mu$) and standard deviation ($\sigma_w$) 
parameters of $W_t$ are~1. The lag-1
autocorrelation coefficient ($\rho$) is not invariant to the
transformation,\citep{hofert2018elements} but its value can be obtained by
\begin{equation*}
\int_{-\infty}^\infty \int_{-\infty}^\infty F^{-1}[\Phi(x)] F^{-1}[\Phi(y)] g_2(x, y; \phi) \dd x \dd y - 1,
\end{equation*}
where $g_2(x, y; \phi)$ is the density of a standard bivariate normal
distribution with correlation parameter~$\phi$. We kept the configuration of
$\phi \in \{-0.4, -0.2, 0.0, 0.2, 0.4\}$, and the corresponding lag-1
autocorrelation coefficients are
$\rho \in \{-0.298, -0.156, \allowbreak 0, 0.170, 0.355\}$.

>>>>

We generated time series $X_t$ from a 1st 
order autoregressive (AR(1)) process:
\begin{equation*}
X_t = \phi X_{t-1} + \epsilon_t,
\end{equation*}
where $\phi$ is an autoregressive coefficient, and $\epsilon_t$ is a series of
independent errors from a normal distribution with mean zero and variance
$\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
$\phi$, which was set to five levels: $\{-0.4, -0.2, \allowbreak 0.0, 0.2, 0.4\}$. 
We only
used serial dependences as strong as 0.4, because we only seek to 
establish the 
general trend as the strength of the autocorrelation 
increases, and how it varies depending on the sign of the autocorrelation and 
the parameter of interest. The 
series $X_t$ has mean zero and variance 
$\sigma_x^2 = (1 - \phi^2) \sigma_{\epsilon}^2$, so for each value of $\phi$, we 
set $\sigma_{\epsilon}^2 = 1 / (1 - \phi^2)$ such that $\sigma_x^2 = 1$.

@@

The series were generated by marginally transforming the
AR(1) series $X_t$ in the first simulation study by
\begin{equation*}
W_t = F^{-1}[\Phi(X_t)],
\end{equation*}
where $F^{-1}(p)$ is the quantile function for the unit exponential 
distribution. The true mean ($\mu$) and standard deviation ($\sigma_w$) 
parameters of $W_t$ are~1. The lag-1
autocorrelation coefficient ($\rho$) is not invariant to the
transformation,\citep{hofert2018elements} but its value can be obtained by
\begin{equation*}
\int_{-\infty}^\infty \int_{-\infty}^\infty F^{-1}[\Phi(x)] F^{-1}[\Phi(y)] g_2(x, y; \phi) \dd x \dd y - 1,
\end{equation*}
where $g_2(x, y; \phi)$ is the density of a standard bivariate normal
distribution with correlation parameter~$\phi$. We kept the configuration of
$\phi \in \{-0.4, -0.2, 0.0, 0.2, 0.4\}$, and the corresponding lag-1
autocorrelation coefficients are
$\rho \in \{-0.298, \allowbreak -0.156, 0, 0.170, 0.355\}$.
